Paper 2 !DRAFT! Do not circulate!

### 2014-10-31 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now includes LINEX residual plot.

# Load models
REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
# The function to extract data from the models
extract_data <- function(x, name) {
  # Names are in the form Source.Country.modelType.factor_string
  # Parse various pieces of name
  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
  Source <- name_pieces[[1]]
  Country <- name_pieces[[2]]
  modelType <- name_pieces[[3]]
  factorString <- name_pieces[[4]]
  # Parse the factorString to get the energyType
  energyType <- parseFactorString(factorString)$energyType
  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
             modelType=modelType, energyType=energyType)
}
residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXModel"))
# Bind these all in a data frame. 
residuals_df <- do.call(rbind, residual_data)
# Re-order the factors as desired for our graphs.
residuals_df$Source <- as.factor(
  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
residuals_df$energyType <- as.factor(
  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
@

@@

>>>>

# Load models
REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
# The function to extract data from the models
extract_data <- function(x, name) {
  # Names are in the form Source.Country.modelType.factor_string
  # Parse various pieces of name
  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
  Source <- name_pieces[[1]]
  Country <- name_pieces[[2]]
  modelType <- name_pieces[[3]]
  factorString <- name_pieces[[4]]
  # Parse the factorString to get the energyType
  energyType <- parseFactorString(factorString)$energyType
  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
             modelType=modelType, energyType=energyType)
}
residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXmodel"))
# Bind these all in a data frame. 
residuals_df <- do.call(rbind, residual_data)
# Re-order the factors as desired for our graphs.
residuals_df$Source <- as.factor(
  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
residuals_df$energyType <- as.factor(
  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
@

@@

<<LINEX_Residual_Plot, fig.pos="H", fig.align='center', fig.width=5, fig.height=6, fig.cap="LINEX Residual Plots.">>=
# Use residuals_df to make a graph.
linex_residuals_df <- subset(residuals_df, subset = modelType=="linex")
ggplot(data=linex_residuals_df, aes(x=year, y=resid, color=Source)) + 
  geom_point(size = 1.0) +
  facet_grid(Country ~ energyType) +
  labs(x = "", y = "Residuals") + 
  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
  scale_y_continuous(limits=c(-0.3, 0.2)) +
  xy_theme()
@
